%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

  \cventry
    {Director of Engineering, Developer Monetization} % Job title
    {Roblox} % Organization
    {} % Location
    {January 2026 - Present} % Date(s)
    {
	\begin{cvitems} % Description(s) of tasks/responsibilities
	\item Directed the engineering roadmap and full lifecycle of high-scale transaction systems for one of the world's largest virtual economies, leading an organization of 40 to manage billions of monthly interactions and support revenue generation for millions of developers.
    \item Led a high-performing organization of senior engineers and managers; established rigorous engineering standards and cultural practices for mission-critical monetization infrastructure.
    \item Developed an ML-based platform for code scanning with use cases like: optimize revenue for both the business and creators, ensure compliance with local regulations and internal policies, and optimize developer code to improve game performance and infrastructure resilience.
    \item Partnered with Product, Data Science, and Finance to solve marketplace challenges including fraud prevention and price optimization.
    \item Drove engineering excellence and improved policy posture through hands-on technical contributions.
	\end{cvitems}
    }

  \cventry
    {Senior Director of Engineering, Client and API Foundations} % Job title
    {Pinterest} % Organization
    {} % Location
    {January 2024 - January 2026} % Date(s)
    {
	\begin{cvitems} % Description(s) of tasks/responsibilities
	\item Led an org of 150 people (90 FTEs, 60 contractors) including supervising managers of managers across the USA, Canada, and Mexico.
	\item Directed the strategic modernization of Android, iOS, Web, API, and Design Systems platforms to enhance developer productivity; improve quality and service resilience; and unlock new feature capabilities, positively impacting 750+ internal developers and designers and millions of external customers.
	\item Spearheaded high-impact initiatives including: transition to Swift (iOS), Modern UDF Architecture (Android), AI development standards, unified API schema definitions, comprehensive Accessibility Audit, React 19 migration, API resilience, Graviton EC2 rollout, Web and API unification, Visual Refresh, CI/CD and Metrics modernization - each significantly improving developer velocity, reliability, and operational efficiency.
	\item Acted as incident commander in a company-wide on-call rotation, leading resolution of high-severity incidents. Analyzed trends and facilitated post-mortem reviews to connect teams, promote shared lessons, and drive systemic improvements in service reliability across the company.
	\end{cvitems}
    }

  \cventry
    {Director of Engineering, Client and API Platforms} % Job title
    {} % Organization
    {} % Location
    {June 2022 - January 2024} % Date(s)
    {
	\begin{cvitems} % Description(s) of tasks/responsibilities
	\item Led an org of 50 people across 6 teams: Android Platform, iOS Platform, Web Platform, API Platform, Design Systems, and Product Excellence.
	\item Identified, championed, and drove large-scale initiatives that modernize our clients and API to provide a world-class developer experience.
	\item Scaled the team through both recruiting efforts and growing internal talent.
	\end{cvitems}
    }

  \cventry
    {Director of Engineering} % Job title
    {Twitch} % Organization
    {} % Location
    {July 2021 - June 2022} % Date(s)
    {
	\begin{cvitems} % Description(s) of tasks/responsibilities
	\item Led an org of 21 people with two managers responsible for Mobile Foundations, Viewer Product, and Community Product.
	\item Directly managed the Mobile Foundations team including defining north star vision and developing roadmaps to advance mobile development.
	\item Delivered initiatives like macOS EC2 Migration, Brand Refresh, GraphQL Query Batching support in Apollo, Client Resilience, and Mobile Observability.
	\item Proposed and spearheaded establishing Twitch’s apprenticeship program.
	\end{cvitems}
    }

  \cventry
    {Senior Engineering Manager} % Job title
    {} % Organization
    {} % Location
    {April 2018 - July 2021} % Date(s)
    {
	\begin{cvitems} % Description(s) of tasks/responsibilities
	\item Managed a team of 12 Android and iOS Engineers on 100+ Twitch Viewer and Community infrastructure and customer-impacting projects.
	\item Planned, organized, reviewed technical design, managed execution and risks with cross-functional teams consisting of over 300 people.
	\item Delivered key initiatives like Channel Points by collaborating with engineering, product, and design partners.
	\item Doubled the size of the iOS team in half a year. Hired, mentored, and converted two interns into full-time roles.
	% \item Collaborated with recruiting from sourcing to closing candidates. Standardized and streamlined recruiting process for the entire mobile team: introduced online assessments, interview preparation documents for candidates, and a calibration tool for interviewers.
	\item Formed a company-wide Leadership Book Club: a monthly meeting to discuss leadership and management books.
	% \item Created an employment engagement program for my team to celebrate work anniversaries that has been well-received and subsequently scaled to my entire organization of 200+ people.
	\end{cvitems}
    }

  \cventry
    {Senior Software Engineer} % Job title
    {} % Organization
    {} % Location
    {April 2017 - April 2018} % Date(s)
    {
	\begin{cvitems} % Description(s) of tasks/responsibilities
      	\item Developed features for Ads, Clips, Creator, and VOD on both Android and iOS. Developed a Kotlin DSL-style framework for Android UI testing.
      	\item Led initiatives to improve documentation, continuous integration, build times, tracking validation, and real-time monitoring and alerting.
	\end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Evernote} % Organization
    {} % Location
    {November 2014 - April 2017} % Date(s)
    {
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item Android and iOS developer building delightful apps for note-taking, organizing, and archiving everything used by millions.
    % \item {One of eight Android engineers building a delightful app for note-taking, organizing, and archiving everything used by millions.}
		\item {Led client-side prototyping of a library to deliver rich, interactive messages without requiring an app update.}
	% \item {iOS development (Objective-C \& Swift) on key features including Google Sign-In and a server-driven message delivery library.}
	% \item {Developed award-winning Hack Week project that allows employees to give feedback on company-catered meals. This project is  deployed in Redwood City, Austin, and Zurich.}
	% \item {Supported talent development: new employee onboarding, interview panelist, and initiatives to promote cross-team collaboration.}
	% \item {Led community-building events: emcee for biweekly company-wide demo days, coding workshops for non-engineers, Hack Week planning, and coordinating monthly tech talks.}
	%	\item {Led community-building events: emcee for company-wide demo days, coding workshops for non-engineers, and Hack Week planning.}
	\end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Smule} % Organization
    {} % Location
    {August 2010 - August 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item {iOS development (2010 - 2012), Android development (2012 - 2014), and CI / CD on Ocarina, Magic Piano, Magic Fiddle, and Sing Karaoke.}
       % \item {Android development (2012 - 2014) on Sing Karaoke and Magic Piano.}
       % \item {iOS development (2010 - 2012) on Magic Piano, Ocarina, I Am T-Pain, Magic Fiddle, and Glee.}
       %  \item {Led development of the first release of Sing Karaoke for Android, including a major update that introduced a full design update of the app.}
       %  \item {Managed the Android shared codebase, used across three projects.}
      \item {Managed hardware and software platform for continuous integration and release engineering for Android and iOS.}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
