%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Evernote} % Organization
    {Redwood City, California} % Location
    {November 2014 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Android development on Evernote for Android - 4.6 / 5 stars, millions of installs.}
        \item {Led client development of a library to deliver messages without requiring an app update.}
        \item {Hired gun for iOS development (Objective-C and Swift) on key initiatives including Google Sign In and integrating message delivery engine.}
		\item {Onboarding new team members, emceeing biweekly demo days, leading coding workshops for non-engineers, Hack Week planning committee member, and coordinating monthly tech talks.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Smule} % Organization
    {San Francisco, California} % Location
    {August 2010 - August 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Android development (2012 - 2014) on Sing Karaoke and Magic Piano.}
        \item {iOS development (2010 – 2012) on Magic Piano, Ocarina, I Am T-Pain, Magic Fiddle, and Glee.}
        \item {Led development of the first release of Sing Karaoke for Android, as well as the release of a major update introducing a full design update of the product.}
        \item {Manage and maintain the Android team’s shared codebase, used across three projects.}
        \item {Experienced with continuous integration and release engineering through TeamCity and Jenkins for iOS and Android.}
      \end{cvitems}
    }
    
%---------------------------------------------------------

\end{cventries}
